ins---
title: "Lab 10 - Grading the professor, Pt. 1"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

## Load Packages and Data

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
library(broom)
library(viridis)
library(ggplot2)

```

## Exercise 1

*Provide your answer here.*  
Add code chunks as needed. Don't forget to label your code chunks.


```{r exercise1_code}
# Add your R code here

data("evals")
view(evals)

evals$prof_id <- as.factor(evals$prof_id)

```

```{r plot}
ggplot(evals, aes(x = reorder(course_id, score), y = score)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Bar Chart of Score by Course (Ordered by Score)",
    x = "Evaluations Ordered From Lowest to Highest",
    y = "Attractiveness Score")+
  theme_classic() +
  theme(axis.text.x = element_blank(),   # Remove x-axis labels
    axis.ticks.x = element_blank())
  
```

Yes the distribution appears to be skewed such that there is a positive skew. Most professors recieved a positive score (above 3).

This mostly fits what I would expect. Most professors get pretty good scores but their ratings seem to drop more sharply below a rating of 3--likely because if they are notably bad, students are more likely to agree that they are that bad.

## Exercise 2

"Create a scatterplot of score versus bty_avg (a professor’s average beauty rating). Describe any pattern you observe—does there appear to be a trend, clustering, or wide variation? Don’t overthink it; just describe what you see."

```{r scatterplot}
ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_point() +
  labs(
    title = "Scatterplot of Score vs. Beauty Average",
    x = "Beauty Average",
    y = "Score") +
  theme_classic()
```
It seems that beauty does correlate with evaluation scores, especially when you look at the lower scores. It seems that if a professor is more attractive, they are less likely to recieve a lower score. Beauty does not seem to effect higher scores (ceiling effect?).

##Exercise 3

```{r jitter}
ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_jitter() +
  labs(
    title = "Scatterplot of Score vs. Beauty Average",
    x = "Beauty Average",
    y = "Score") +
  theme_classic()
```
This reveals all the clusters that were obscured in the previous graph because the points were stacked on one another. I don't think this changes too much about the interpretation however, it visually emphasized the correlation I described earlier.

##Exercise 4
"Let’s see if the apparent trend in the plot is something more than natural variation. Fit a linear model called m_bty to predict average professor evaluation score by average beauty rating (bty_avg). Based on the regression output, write the linear model."

```{r regression}
m_bty <- lm(score ~ bty_avg, data = evals)
summary(m_bty)
```
The linear model is: score = 3.88 + b0.067

*Provide your answer here.*  
Add code chunks as needed.

```{r exercise2_code}
# Add your R code here
```

## Additional Exercises

*Repeat the format above for additional exercises.*

## Hint

For Exercise 12, the `relevel()` function can be helpful!
